Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-08-04 tex/ms.tex
fix corner plot figure labels
alternative \Delta formulation

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, \excluster, using the full YY-band
photometry. In Figure \ref{fig:inferred_spectrum} we show the spectra
that result from draws of the parameters $[\theta,\alpha]$ from the
posterior distribution, as well as several of the individual
components of the model constructed from each draw. Figure
\ref{fig:inferred_spectrum} also shows the calibrated spectrum on
which the priors were conditioned, and residuals between the posterior
models and the observed data.  The agreement is quite good, though
some lines are not accurately predicted.  For example, the observed
Mg$b$ absorption appears stronger than the modeled absorption.

>>>>

XXX Alternative XXX.
Because the model  of equation \ref{eq:spectroscopicLF} includes an
additive term in the form of the residual column vector $\Delta$,
sharp spectral features can be diluted. To mitigate this we try a
model where the residual column vector is taken to be the residual
\emph{from the calibration vector $f(\alpha)$}.  That is, 
\begin{eqnarray}\label{eq:spectroscopicLFalt}
\Delta &\equiv& \frac{d}{\mu(\theta)} - f(\alpha)
\quad ,
\end{eqnarray}

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, \excluster, using the full YY-band
photometry. In Figure \ref{fig:inferred_spectrum} we show the spectra
that result from draws of the parameters $[\theta,\alpha]$ from the
posterior distribution, as well as several of the individual
components of the model constructed from each draw. Figure
\ref{fig:inferred_spectrum} also shows the calibrated spectrum on
which the priors were conditioned, and residuals between the posterior
models and the observed data.  The agreement is quite good, though
some lines are not accurately predicted.  For example, the observed
Mg$b$ absorption appears stronger than the modeled
absorption. {\color{blue} Should I show blowups of selected regions/lines?}
